A Hitchhiker's Guide to Reproducible Research in R

### 2021-07-12 manuscript.Rmd
added some lines wrt Caspar's point #5 later on

# Tutorial

@@

This information makes internal dependencies to other files in the project and external dependencies to R packages explicit.
`repro` can use this information to infer a Makefile for the dependencies on other files and a Dockerfile that includes all required packages.
In everyday work, the simplest solution is to now call the function `repro::automate()` which both creates a Makefile and a Dockerfile from all R Markdown files in the project (all files with the ending `.Rmd`) based on the respective repro metadata entries.
Every time you change the `repro`-metadata, change the output format, or add a new R Markdown file to the project, the Makefile and Dockerfile are potentially outdated, and you should run `repro::automate()` to keep them up to date.
The function `repro::automate()` does not overwrite manual changes, and there is no harm in running it too often.
Other than the Makefile and the Dockerfile, which are created in the document root path, repro generates a few more files in the `.repro` directory (which we will explain in detail later), all of which you should add and commit to Git. <!--AB: why is this addition not automated? Feels strange given that this is our recommended best practice?!-->

>>>>

# Creating reproducible research projects

@@

This information makes internal dependencies to other files in the project and external dependencies to R packages explicit.
`repro` can use this information to infer a Makefile for the dependencies on other files and a Dockerfile that includes all required packages.
These two files together form the basis for consistency within a research project and consistency across different systems.
At this point, we would like to emphasize that a preqrequisite for reproducibility is that every step taken in an analysis can be automatically reproduced.
This means there must be no manual processing such as copy and pasting, manual modification of data files (e.g., manually removing observations or manually recoding variables). 
Ideally, all data preprocessing is well-documented and gathered in a separate R file, which is then called before a Markdown report is generated (that is, the preprocessing script is added in the metadata header under _scripts:_).
In everyday work, the simplest solution is to now call the function `repro::automate()` which both creates a Makefile and a Dockerfile from all R Markdown files in the project (all files with the ending `.Rmd`) based on the respective repro metadata entries.
Every time you change the `repro`-metadata, change the output format, or add a new R Markdown file to the project, the Makefile and Dockerfile are potentially outdated, and you should run `repro::automate()` to keep them up to date.
The function `repro::automate()` does not overwrite manual changes, and there is no harm in running it too often.
Other than the Makefile and the Dockerfile, which are created in the document root path, repro generates a few more files in the `.repro` directory (which we will explain in detail later), all of which you should add and commit to Git. <!--AB: why is this addition not automated? Feels strange given that this is our recommended best practice?!-->
